### 2014-07-16 paper.tex
reformatted other sections

Many studies have reported strong associations between MHC alleles and
resistance or susceptibility to MD.  For example, chickens with MHC allele
B$^{21}$ are highly resistant in contrast to chickens with B$^{16}$ allele which
are highly susceptible.  ADOL lines 6 and 7, both share (B$^{2}$) allele, yet
exhibit different phenotypic responses to MD; e.g., challenge with JM/102W
strain with result in 0 and 100\% MD incidence for lines 6 and 7, respectively.
Thus, the major unanswered questions are what genetic factors, especially those
that are non-MHC, contribute to susceptibility and resistance of the disease and
what is the main contributing mechanism.

In the past decades, significant efforts have been spent to study variations in
a global gene expression between resistant and susceptible birds using
microarray and RNA-Seq methods in order to identify non-MHC genes that
contribute to resistance to MD~\cite{}.  However, none of the studies have
investigated differential expression of alternative isoforms, which are known to
play a significant role in many biological events including immune responses.
In addition, studies have shown that isoform expression levels can provide
better signatures for some diseases~\cite{zhang2013isoform}.  Changes of isoform
expression levels are governed partly by two types of {\em cis-}regulatory
elements: Exon Splicing Enhancer (ESE) and Exon Splicing Silencer (ESS), which
are located within an exon sequence.  A number of sequence motifs of ESE and ESS
have been identified in human and some other organisms and could be predicted
{\em in silico}.  Mutations that disrupt or create those motifs could alter
splicing patterns leading to aberrant alternative splicing.  A number of
disease-associated single-nucleotide polymorphsims in coding regions (cSNPs)
that affect ESEs and ESSs have been well characterized~\cite{blencowe2000exonic,
wang2007splicing}.
%In fact, 15\% of mutations that cause genetic diseases affect pre-mRNA splicing
%via this mechanism.
Therefore, variations in isoform expression could lead to identification of SNPs
that underlie genetic resistance to MD.  In this article, we reported
differential-expressed genes and isoforms that may contribute to resistance to
MD as well as cSNPs that can potentially affect isoform expression levels.

@@

\subsection*{Differential expression suggests inactive adaptive immune responses
in line 6}

@@

\subsection*{Functional analysis of differential-expressed genes}

@@

At this stage of infection, our results suggest that lytic infection of MDV
stimulates both innate and adaptive immune responses, which leads to activation
of T cells in line 7.  Only activated T cells are infected by MDV, therefore,
the lytic phase could facilitate the spread of the viruses by enhancing
expansion of activated T cells.  Due to cell-associate nature of MDV, the
viruses transfer to T cells via cell-to-cell contact between B cells and T cells
during antigen presentation or B cells activation by T helper cells.  Therefore,
it is beneficial for the host to restrain such contact.  However, it is not
clear how chickens in line 6 control the lytic infection of MDV.
% Two mechanisms have been speculated to contribute to MD resistance.
% First innate immune responses could be highly effective and could activate
% strong adaptive immune responses that rapidly control viral replication and force the viruses to undergo latent phase.
% Second, innate immune resposnes itself could be highly effective in limiting viral replication~\cite{smith2011systems}.

@@

Group III (Table~\ref{tab:line67i_diff_line67u_three}) includes genes that
exhibit differential isoform expression only in infected line 7.  A number of
genes in this group encode proteins that are parts of spliceosome: {\em SRSF3},
{\em HNRNPDL}, {\em SFSWAP}, {\em THOC1}, {\em RNPC3} and {\em SRSF5}.  Two
genes involved in cell-cell contact regulated by integrins are also in this
group.  {\em PPP1R12A} is a myosin phosphatase that regulates the interaction of
actin and myosin downstream of GTPase Rho proteins.  {\em PODXL} encodes
PODX-like protein that functions in integrin-dependent manner as both
pro-adhesive and anti-adhesive molecules.  This protein is involved in
cell-to-cell contact, cell trafficking, and cancer progression~\cite{}.

@@

\subsubsection*{Roles of {\em LFA-1} and actin cytoskeleton pathway in T cells
activation}

Integrins are a special kind of receptors that transmit signals bidirectionally
across the cell membrane.  They are heterodimeric composed of an $\alpha$
(large) and a $\beta$ (small) subunits~\cite{wang2010immunopathologies}.
$\beta_{2}$ (CD18) subunit encoded by {\em ITGB2} is expressed on lymphocytes
and antigen presenting cells (APCs) as a component of {\em LFA-1} and {\em CR3}
receptors.  LFA-1 binds to its ligand ICAM-1 to help form a synapse that bring
APC and T cell together to initiate antigen presentation leading to T cell
activation~\cite{dustin2000immunological}.  Absence of LFA-1 leads to impaired
functions of lymphocytes in proliferation and tumor
rejection~\cite{scharffetter1998spontaneous,schmits1996lfa}.  Mutations in {\em
ITGB2} gene has been associated with type 1 leukocyte adhesion deficiency
(LAD-1), an autosomal-recessive inherited disease found in few families.  The
disease is characterized by impair of lymphocytes in adherent-dependent
functions, lack of accumulation to the site of infection and recurrent bacterial
and fungal infection~\cite{springer1987lymphocyte}.

Actin cytoskeleton is very important in T cell activation because it enhances
activity of LFA-1 by increasing its avidity and recruiting signaling molecules
necessary for downstream signaling~\cite{dustin2000immunological,
van2000avidity}.  Cytoskeleton proteins binding to cytoplasmic domain of LFA-1
are thought to play an important role in driving LFA-1 to aggregation on the
cell surface, resulting in increased avidity.  Aggregation of LFA-1 has been
demonstrated to be essential for lymphocytes to bind to the
ligand~\cite{van1994extracellular}.  Interestingly, {\em RAC3, PFN2,} and {\em
PPP1R12A}, which are involved in actin cytoskeleton pathway
(Figure~\ref{kegg_actin}), also expressed different ratios of alternative splice
forms between lines 6 and 7.  Some of these genes are also co-present in three
other pathways that involved in immune responses (Table~\ref{tab:integrin}).
This could be speculated that pre-mRNA splicing of these genes is co-regulated
by splicing regulators or some genetic factors.

Using exon-centric approach, we identified several genes involved in actin
cytoskeleton, especially {\em ITGB2}, that expressed different ratios of
alternative isoforms between lines 6 and 7.  As described above, {\em ITGB2}
encodes $\beta$-subunit of integrins including LFA-1, which exclusively
expressed in lymphocytes and plays a major role in lymphoproliferation, antigen
presentation, T cells activation, and cytotoxicity.  In patients with LFA-1
deficiency (LAD), the response of lymphocytes to mitogens is
decreased~\cite{springer1987lymphocyte}.  The decrease in responsiveness to
mitogens have been shown to correlate with resistance to MD by Lee and
Bacon~\cite{lee1983ontogeny}, who illustrated that resistant birds (line 6 and
N) were less responsive to phytohemagglutinin (PHA) than susceptible birds (line
7 and P).

@@

Interestingly, by grouping genes based on patterns of $\Psi$s, we found that
many genes in group II: {\em ITGB2, PFN2, DYNLL2, DYNLT1, SEPT11}, and {\em
ZDHHC7}, are involved in cytokinesis or cell synapse, which are important for
aggregation of LFA-1 and T cell activation as discussed above.  The $\Psi$
values in group II are more similar within line than between lines in both
control and infected groups, suggesting the possibility that the alternative
splicing is controlled by a genetic mechanism.  Based on the independent
criteria, enrichment of cytoskeletal genes in this group could not be just a
mere coincidence, but an evidence suggesting that inefficiency of T cell
activation in line 6 is linked to a genetic factor that regulate alternative
splicing of {\em ITGB2} and other genes in the cytoskeleton system.
Experimental validation of exonic SNPs provided by this study could shed some
lights on underlying polymorphisms that contribute to MD resistance.

\subsubsection*{Protein domains}

To understand the role of the alternative splice forms on the function of these
genes, transcripts were translated to protein sequences by
ESTscan~\cite{iseli1999estscan}.  Protein sequences were then searched for
annotated protein domains using the standalone version of InterPro
Scan~\cite{quevillon2005interproscan}.  Besides {\em ITGB2}, other genes have
alternative exons located in coding regions and could potentially affect
functional protein domains in some ways.  The exon with alternative 3$\prime$
splice site of {\em RAC3} encode part of a protein domain identified as small
GTPase of Ras subfamily (ProSiteProfiles:PS5142 and SMART:SM00173).  Rac3 is
highly homologous to Rac1 and has been reported to possess the ability of
promoting membrane ruffling, transformation, activation of c-Jun transcriptional
activity and a co-activator of NF$\kappa$B~\cite{,werbajh2000rac}.  Activated
Rac also regulates production of superoxide in neutrophils and macrophages.

@@

\subsubsection*{Prediction of {\em cis}-regulatory elements in alternative
splicing exons}

Although alternative splicing of genes in all groups could be regulated by {\em
cis-} and {\em trans-}splicing factors, genes in group II are more likely to be
regulated by {\em cis-}regulatory factors.  The ratios of isoform expression in
this group were relatively stable within line, but were significantly different
between lines.  Investigation of nucleotide differences within exons of line 6
and 7 could reveal a possible role of cSNPs in regulating alternative splicing
in this group.  We obtained a sequence of an alternative exon from line 6 and
used Human Splicing Finder (HSF) to determine whether SNPs from line 7 could
alter predicted ESEs or ESSs.  Results from some genes involved in cytokinesis
are discussed in this section.  Exonic SNPs from line 6 and 7 are listed in
Table~\ref{tab:deu_snps}.

For {\em ITGB2}, a SNP (T) at position 26 of the cDNA from line 6, which
corresponds to position 7,183,696 on chromosome 7 is located in a predicted
binding site for SC35, which is an exon enhancer.  Although the exon is not
expressed in line 7, we found that there is no polymorphisms between lines 6 and
7 according to SNPs data from the genome resequencing.  Therefore, this SNP may
not be accounted for exclusion of the exon in line 7 (Figure~\ref{itgb2}).

Exon sequences of {\em PFN2} from line 6 and 7 differ at position 2,072 on cDNA
or 23,221,934 on chromosome 9.  A small insertion of two AA nucleotides is
predicted to create a new binding site for Tra2-$\beta$ splicing regulator,
which serves as a stabilizer of an enhancer complex~\cite{lopez1998alternative}.
From exon expression data, $\Psi$ of an exon with alternative splicing increases
from 0.20-0.30 to about 0.50 in line 7.  Tra2 could possibly increase inclusion
of the exon with alternative 3$\prime$ splice site via ESE-dependent 3$\prime$
splice site activation (Figure~\ref{pfn2}).  Even though the linear distance
between Tra2-$\beta$ binding site and the alternative 3$\prime$ splice site is
greater than 1kb, Tra2 could possibly get close to the 3$\prime$ splice site in
the secondary structure of the mRNA.

Replacement of A with G nucleotide in the skipped exon of {\em DYNLL2} from line
6 is predicted to slightly alter the binding site of several ESEs as well as to
create a new binding site for 9G8.  This exon is upregulated in line 7 compared
to line 6, therefore, the present of the new binding site for 9G8 exon enhancer
helps support the expression results.  In addition, A nucleotide is this
position matches the reference nucleotide, therefore, we could expect this exon
to be expressed in other datasets.  According to EST tags on the UCSC genome
browser, the exon has been found and sequenced from chicken eyes (15d
post-hatched, EST sequence:DR424100).

For {\em DYNLT1}, the skipped exon was absent in line 7, therefore, we could not
determine the SNPs from RNA-Seq data.  However, data from DNA resequencing
showed that there was a polymorphism at position 51,357,865 on chromosome 3.
Replacing G with C from line 7 is predicted to slightly alter predicted binding
sites for 9G8 as well as SRp55 exon enhancer.  However, whether the alteration
down regulates the exon in line 7 is unclear.

There are too many SNPs in the exon of {\em SEPT11} and {\em ZDHHC7}, making it
unfeasible to predict which SNP regulates the exon expression.  Therefore, we do
not discuss these two genes in this section.  However, results from HSF analysis
of these two genes and other genes in this group are provided in the
supplementary materials.

@@

% However, to mechanism that contribute to resistance to MD could be very
% complex and integration of global gene expression data as well as experimental
% data from different stages of infection will be required to fully elucidate.
% Moreover, better gene models and a reference genome will be necessary.

% You may title this section "Methods" or "Models". 
% "Models" is not a valid title for PLoS ONE authors. However, PLoS ONE
% authors may use "Analysis" 
\section*{Materials and Methods}
\subsection{Gene Models Construction}

Due to lack of complete gene models for chickens, we employed two methods to
construct gene models from RNA-Seq reads.  First, short reads were quality
trimmed with conditri/2.1~\cite{} and assembled using Velvet/1.21~\cite{} and
Oases/0.2.06~\cite{} to obtain long transcripts.  Assembly was done with hash
lengths range from 21 to 31 for both local and global assembly (described in
Gimme paper).  Poly-A tails were trimmed and low complexity transcripts were
removed by Seqclean~\cite{}.  All transcripts were then aligned to chicken
reference genome (galGal4, with unplaced and random chromosomes removed) with
BLAT~\cite{}.  Second, reads were aligned to reference genome using
Tophat/2.0.5~\cite{} and ENSEMBLE gene models release 73 was used to guide
reference-based assembly by Cufflinks2~\cite{}.  Alignments from BLAT and models
from Cufflinks were then combined to construct gene models by Gimme (manuscript
in preparation).

\subsection{Differential Gene Expression and Gene Ontology}

@@

\subsection{Differential Splicing Event}

@@

\subsection{Variant Calling and {\em In Silico} Splicing Analysis} Variants were
called using mpileup command from SAMTools/0.1.18~\cite{} and BCFTools~\cite{}.
Only variants with quality score $\ge20$ were used for mutation analyses.  Exon
enhancers and suppressors were predicted using Human Splicing Finder web
portal~\cite{}.  Human default parameter settings were used in all analyses.
The following regulatory sequences were used to determined the effect of
variants: HSF integrated matrices for serine/arginine-rich proteins (SRp40,
SC35, SF2/ASF, SF2/ASF, IgM/BRCA1, and SRp55), exonic splicing enhancer (ESE),
RESCUE-ESE hexamer (RESCUE-ESE), putative 8-mer ESEs (PESEs) and putative 8-mers
exonic splicing silencers (PESSs), exon-identity and intron-identiry elements
(EIEs and IIEs), hetronuclear ribonucleoprotein-binding motifs, and Fas exonic
splicing silencers.

\subsection{Protein domains search}

>>>>

Many studies have reported strong associations between MHC alleles and
resistance or susceptibility to MD.  For example, chickens with MHC allele
B\textsuperscript{21} are highly resistant in contrast to chickens with
B\textsuperscript{19} allele which are highly susceptible.  ADOL lines 6 and 7,
both share (B\textsuperscript{2}) allele, yet exhibit different phenotypic
responses to MD; e.g., challenge with JM/102W strain with result in 0 and 100\%
MD incidence for lines 6 and 7, respectively.  Thus, the major unanswered
questions are what genetic factors, especially those that are non-MHC,
contribute to susceptibility and resistance of the disease and what is the main
contributing mechanism.

In the past decades, significant efforts have been spent to study variations in
a global gene expression between resistant and susceptible birds using
microarray and RNA-Seq methods in order to identify non-MHC genes that
contribute to resistance to
MD~\cite{sarson2008transcriptional,morgan2001induction,vallejo1998genetic,yonash1999high,bumstead1998genomic}.
However, none of the studies have investigated differential expression of
alternative isoforms, which are known to play a significant role in many
biological events including immune responses.  In addition, studies have shown
that isoform expression levels can provide better signatures for some
diseases~\cite{zhang2013isoform}.  Changes of isoform expression levels are
governed partly by two types of {\em cis-}regulatory elements: Exon Splicing
Enhancer (ESE) and Exon Splicing Silencer (ESS), which are located within an
exon sequence.  A number of sequence motifs of ESE and ESS have been identified
in human and some other organisms and could be predicted {\em in silico}.
Mutations that disrupt or create those motifs could alter splicing patterns
leading to aberrant alternative splicing.  A number of disease-associated
single-nucleotide polymorphsims in coding regions (SNPs) that affect ESEs and
ESSs have been well characterized~\cite{blencowe2000exonic, wang2007splicing}.
%In fact, 15\% of mutations that cause genetic diseases affect pre-mRNA splicing
%via this mechanism.
Therefore, variations in isoform expression could lead to identification of SNPs
that underlie genetic resistance to MD.  In this article, we reported
differential-expressed genes and isoforms that may contribute to resistance to
MD as well as SNPs that can potentially affect isoform expression levels.

@@

\subsection*{Differential gene expression indicates active immune responses to
ongoing lytic infection in line 7}

@@

\subsection*{Functional analysis of differential-expressed genes indicates
inactive adaptive immune responses in line 6}

@@

At this stage of infection, our results suggest that lytic infection of MDV
stimulates both innate and adaptive immune responses, which leads to activation
of T cells in line 7.  Only activated T cells are infected by MDV, therefore,
the lytic phase could facilitate the spread of the viruses by enhancing
expansion of activated T cells.  Due to cell-associate nature of MDV, the
viruses transfer to T cells via cell-to-cell contact between B cells and T cells
during antigen presentation or B cells activation by T helper cells.  Therefore,
it is beneficial for the host to restrain such contact.  However, it is not
clear how chickens in line 6 control the lytic infection of MDV.  Two mechanisms
have been speculated to contribute to MD resistance.  First innate immune
responses could be highly effective and could activate strong adaptive immune
responses that rapidly control viral replication and force the viruses to
undergo latent phase.  Second, innate immune resposnes itself could be highly
effective in limiting viral replication~\cite{smith2011systems}.

@@

Group III (Table~\ref{tab:line67i_diff_line67u_three}) includes genes that
exhibit differential isoform expression only in infected line 7.  A number of
genes in this group encode proteins that are parts of spliceosome: {\em SRSF3},
{\em HNRNPDL}, {\em SFSWAP}, {\em THOC1}, {\em RNPC3} and {\em SRSF5}.  Two
genes involved in cell-cell contact regulated by integrins are also in this
group.  {\em PPP1R12A} is a myosin phosphatase that regulates the interaction of
actin and myosin downstream of GTPase Rho proteins.  {\em PODXL} encodes
PODX-like protein that functions in integrin-dependent manner as both
pro-adhesive and anti-adhesive molecules.  This protein is involved in
cell-to-cell contact, cell trafficking, and cancer
progression~\cite{nielsen2009role,somasiri2004overexpression}.

@@

\subsection*{Roles of {\em LFA-1} and actin cytoskeleton in T cells
activation}

By grouping genes based on patterns of $\Psi$s, we found that many genes in
group II: {\em ITGB2, PFN2, DYNLL2, DYNLT1, SEPT11}, and {\em ZDHHC7}, are
involved in cytokinesis or cell synapse, which are important for T cell
activation.  As described above, {\em ITGB2} encodes $\beta$-subunit of
integrins including LFA-1, which exclusively expressed in lymphocytes and plays
a major role in lymphoproliferation, antigen presentation, T cells activation,
and cytotoxicity.  Integrins are a special kind of receptors that transmit
signals bidirectionally across the cell membrane.  They are heterodimeric
composed of an $\alpha$ (large) and a $\beta$ (small)
subunits~\cite{wang2010immunopathologies}.  $\beta_{2}$ (CD18) subunit encoded
by {\em ITGB2} is expressed on lymphocytes and antigen presenting cells (APCs)
as a component of {\em LFA-1} and {\em CR3} receptors.  LFA-1 binds to its
ligand ICAM-1 to help form a synapse that bring APC and T cell together to
initiate antigen presentation leading to T cell
activation~\cite{dustin2000immunological}.

Absence of LFA-1 leads to impaired functions of lymphocytes in proliferation and
tumor rejection~\cite{scharffetter1998spontaneous,schmits1996lfa}.  Mutations in
{\em ITGB2} gene has been associated with type 1 leukocyte adhesion deficiency
(LAD-1), an autosomal-recessive inherited disease found in few families.  The
disease is characterized by impair of lymphocytes in adherent-dependent
functions, lack of accumulation to the site of infection and recurrent bacterial
and fungal infection~\cite{springer1987lymphocyte}.  In addition, the response
of lymphocytes to mitogens is decreased in patients with
LAD~\cite{springer1987lymphocyte}.  The decrease in responsiveness to mitogens
have been shown to correlate with resistance to MD by Lee and
Bacon~\cite{lee1983ontogeny}, who illustrated that resistant birds (line 6 and
N) were less responsive to phytohemagglutinin (PHA) than susceptible birds (line
7 and P).

Actin cytoskeleton is very important in T cell activation because it enhances
activity of LFA-1 by increasing its avidity and recruiting signaling molecules
necessary for downstream signaling~\cite{dustin2000immunological,
van2000avidity}.  Cytoskeleton proteins binding to cytoplasmic domain of LFA-1
are thought to play an important role in driving LFA-1 to aggregation on the
cell surface, resulting in increased avidity.  Aggregation of LFA-1 has been
demonstrated to be essential for lymphocytes to bind to the
ligand~\cite{van1994extracellular}.  Interestingly, {\em RAC3, PFN2,} and {\em
PPP1R12A}, which are involved in actin cytoskeleton pathway
(Figure~\ref{kegg_actin}), also expressed different ratios of alternative splice
forms between lines 6 and 7.  Some of these genes are also co-present in three
other pathways that involved in immune responses (Table~\ref{tab:integrin}).
It could be speculated that pre-mRNA splicing of these genes is co-regulated
by splicing regulators or some genetic factors.

\subsection*{Prediction of functional domains of splice forms of genes in the
actin cytoskeleton pathway}

To predict the function of the alternative splice forms of genes in actin
cytoskeleton pathway, transcript sequences were translated to protein sequences
by ESTscan~\cite{iseli1999estscan}.  Protein sequences were then searched for
annotated protein domains using the standalone version of InterPro
Scan~\cite{quevillon2005interproscan}.  Besides {\em ITGB2}, other genes have
alternative exons located in coding regions and could potentially affect
functional protein domains in some ways.  The exon with alternative 3$\prime$
splice site of {\em RAC3} encode part of a protein domain identified as small
GTPase of Ras subfamily (ProSiteProfiles:PS5142 and SMART:SM00173).  Rac3 is
highly homologous to Rac1 and has been reported to possess the ability of
promoting membrane ruffling, transformation, activation of c-Jun transcriptional
activity and a co-activator of NF$\kappa$B~\cite{werbajh2000rac}.  Activated Rac
also regulates production of superoxide in neutrophils and macrophages.

@@

@@

\subsection*{Prediction of {\em cis}-regulatory elements in alternative
splicing exons of genes in group II}

Although alternative splicing of genes in all groups could be regulated by {\em
cis-} and {\em trans-}splicing factors, genes in group II are more likely to be
regulated by {\em cis-}regulatory factors.  The ratios of isoform expression in
this group were relatively stable within line, but were significantly different
between lines.  Investigation of nucleotide differences within exons of lines 6
and 7 could reveal a possible role of SNPs in regulating alternative splicing in
this group.  We obtained a sequence of an alternative exon from line 6 and used
Human Splicing Finder (HSF) to determine whether SNPs from line 7 could alter
predicted ESEs or ESSs.  Results from some genes involved in cytokinesis are
discussed in this section.  Exonic SNPs from line 6 and 7 are listed in
Table~\ref{tab:deu_snps}.

For {\em ITGB2}, a SNP (T) at position 26 of the cDNA from line 6, which
corresponds to position 7,183,696 on chromosome 7 is located in a predicted
binding site for SC35, which is an exon enhancer.  Although the exon is not
expressed in line 7, we found that there is no polymorphisms between lines 6 and
7 according to SNPs data from the genome resequencing.  Therefore, this SNP may
not be accounted for exclusion of the exon in line 7 (Figure~\ref{itgb2}).  Exon
sequences of {\em PFN2} from line 6 and 7 differ at position 2,072 on cDNA or
23,221,934 on chromosome 9.  A small insertion of two AA nucleotides is
predicted to create a new binding site for Tra2-$\beta$ splicing regulator,
which serves as a stabilizer of an enhancer complex~\cite{lopez1998alternative}.
From exon expression data, $\Psi$ of an exon with alternative splicing increases
from 0.20-0.30 to about 0.50 in line 7.  Tra2 could possibly increase inclusion
of the exon with alternative 3$\prime$ splice site via ESE-dependent 3$\prime$
splice site activation (Figure~\ref{pfn2}).  Even though the linear distance
between Tra2-$\beta$ binding site and the alternative 3$\prime$ splice site is
greater than 1kb, Tra2 could possibly get close to the 3$\prime$ splice site in
the secondary structure of the mRNA.

Replacement of A with G nucleotide in the skipped exon of {\em DYNLL2} from line
6 is predicted to slightly alter the binding site of several ESEs as well as to
create a new binding site for 9G8.  This exon is upregulated in line 7 compared
to line 6, therefore, the present of the new binding site for 9G8 exon enhancer
helps support the expression results.  In addition, A nucleotide is this
position matches the reference nucleotide, therefore, we could expect this exon
to be expressed in other datasets.  According to EST tags on the UCSC genome
browser, the exon has been found and sequenced from chicken eyes (15d
post-hatched, EST sequence:DR424100).  For {\em DYNLT1}, the skipped exon was
absent in line 7, therefore, we could not determine the SNPs from RNA-Seq data.
However, data from DNA resequencing showed that there was a polymorphism at
position 51,357,865 on chromosome 3.  Replacing G with C from line 7 is
predicted to slightly alter predicted binding sites for 9G8 as well as SRp55
exon enhancer.  However, whether the alteration down regulates the exon in line
7 is unclear.

There are too many SNPs in the exon of {\em SEPT11} and {\em ZDHHC7}, making it
unfeasible to predict which SNP regulates the exon expression.  Therefore, we do
not discuss these two genes in this section.  However, results from HSF analysis
of these two genes and other genes in this group are provided in the
supplementary materials.  Experimental validation of exonic SNPs provided by
this study could shed some lights on underlying polymorphisms that contribute to

@@

% You may title this section "Methods" or "Models". 
% "Models" is not a valid title for PLoS ONE authors. However, PLoS ONE
% authors may use "Analysis"
\section*{Materials and methods}

\subsection{Sequences and quality trimming}

mRNAs were extracted from spleens of control and infected chickens lines 6 and 7
(4 d.p.i).  Sequence libraries were prepared by standard Illumina unstranded
single- and paired-end protocols.  Library size of the paired-end datasets is
approximately 175 bp.  Read lengths are 75 bp in both single- and paired-end
libraries.  Reads were quality trimmed by Condetri 2.1~\cite{smeds2011condetri}
with quality score cutoff of 30.  The first 10 bases were removed due to
non-uniform distribution of nucleotides.

\subsection*{Gene models construction}

Due to lack of complete gene models for chickens, we employed two methods to
construct gene models from RNA-Seq reads.  First, short reads were assembled
using Velvet/1.2.03~\cite{Zerbino:2008vu} and Oases/0.2.06~\cite{Schulz:2012je}
to obtain long transcripts.  Assembly was done with hash lengths range from 21
to 31 for both local and global assembly (described in Gimme paper).  Poly-A
tails were trimmed and low complexity transcripts were removed by
Seqclean~\cite{seqclean}.  All transcripts were then aligned to chicken
reference genome (galGal4, with unplaced and random chromosomes removed) with
BLAT~\cite{Kent:2002tv}.  Second, reads were aligned to reference genome using
Tophat/2.0.9~\cite{Trapnell:2009dp} and ENSEMBLE gene models release 73 was used
to guide reference-based assembly by Cufflinks2~\cite{Trapnell:2010kd}.
Alignments from BLAT and models from Cufflinks were then combined to construct
gene models by Gimme (manuscript in preparation).

\subsection*{Differential gene expression and gene ontology}

@@

\subsection*{Differential splicing event}

@@

\subsection*{Variant calling and {\em in silico} splicing analysis}

Variants were called using mpileup command from
SAMTools/0.1.18~\cite{li2009sequence} and BCFTools~\cite{bcftools}.  Only
variants with quality score $\ge20$ were used for mutation analyses.  Exon
enhancers and suppressors were predicted using Human Splicing Finder web
portal~\cite{desmet2009human}.  Human default parameter settings were used in
all analyses.  The following regulatory sequences were used to determined the
effect of variants: HSF integrated matrices for serine/arginine-rich proteins
(SRp40, SC35, SF2/ASF, SF2/ASF, IgM/BRCA1, and SRp55), exonic splicing enhancer
(ESE), RESCUE-ESE hexamer (RESCUE-ESE), putative 8-mer ESEs (PESEs) and putative
8-mers exonic splicing silencers (PESSs), exon-identity and intron-identiry
elements (EIEs and IIEs), hetronuclear ribonucleoprotein-binding motifs, and Fas
exonic splicing silencers.

\subsection*{Protein domains search}
